Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls

### 2024-08-22 hello_world/rugsafe/paper/paper.tex
saved

\documentclass{article}
\usepackage{amsmath}

\title{Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls}
\author{info@Rugsafe.org}
\date{v0.0.1 August 1, 2024}

@@

@@

\section{Conclusion}
Rugsafe presents a robust mathematical framework designed to protect against rug pulls in the DeFi space. By combining vault mechanisms, anticoin issuance, and incentive structures, it ensures a secure environment for digital asset management. The protocol's design not only protects users but also opens up new avenues for development and innovation in the DeFi ecosystem.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % Add this line
\usepackage{xcolor}
\pagecolor{black}
\color{white}

\title{Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls}
\author{info@rugsafe.org}
\date{v0.0.1 August 1, 2024}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{images/2.png}
\caption{The inverse logarithmic relationship between the price of the underlying rugged token $C_r$ and the amount of minted anticoins $C_a$. As the price of $C_r$ decreases, the amount of minted $C_a$ increases, providing stability and protection for holders.}
\label{fig:minted_anticoins}
\end{figure}

@@

\section{Closing Remarks}
Rugsafe presents a robust mathematical framework designed to protect against rug pulls in the DeFi space. By combining vault mechanisms, anticoin issuance, and incentive structures, it ensures a secure environment for digital asset management. The protocol's design not only protects users but also opens up new avenues for development and innovation in the DeFi ecosystem.
